```{r appendix, include=FALSE}
```
# Appendix {.tabset}
## *Appendix 1.Decomposition Comparison*

* Classical Decomposition assumes seasonal component repeats from year to year, which usually is not the case in reality, over smoothes rapid rises (is not recommended to use, but still...).
* STL Decomposition is a versatile and robust method that handles any seasonality; seasonal components can change, and smoothness can be controlled.
* X-11 method originated in the US Census Bureau and was further developed by Statistics Canada, based on classical decomposition, a slightly improved version of classical decomposition; the seasonal component varies slowly over time, highly robust to outliers and level shifts in the time series.


## *Appendix 2. Accuracy metrics comparison*
*AIC* criteria are used to assess the goodness of fit of a model, with lower values indicating a better fit.
*RMSE* and MAE are used to measure the difference between predicted values and actual values. Comparatively lower numbers of these metrics assume a better model's forecast quality potential. 

## Plots of all countries' historical data

### **Germany**
```{r}
data_elec %>% autoplot(Germany) + 
  ggtitle("Exports from Switzerland to Germany") +
  ylab("GWt") + xlab("Month")
``` 

### **France**
```{r}
data_elec %>% autoplot(France) + 
  ggtitle("Exports from Switzerland to France") +
  ylab("GWt") + xlab("Month")
```

### **Italy**
```{r}

data_elec %>% autoplot(Italy) + 
  ggtitle("Exports from Switzerland to Italy") +
  ylab("GWt") + xlab("Month")
```

### **Austria**
```{r}
data_elec %>% autoplot(Austria) + 
  ggtitle("Exports from Switzerland to Austria") +
  ylab("GWt") + xlab("Month")
```

### **Lichtenstein**
```{r}
data_elec %>% autoplot(Lichtenstein) + 
  ggtitle("Exports from Switzerland to Lichtenstein") +
  ylab("GWt") + xlab("Month")
```

### **Total**
```{r}
data_elec %>% autoplot(Total) + 
  ggtitle("Exports from Switzerland to All countries") +
  ylab("GWt") + xlab("Month")
```

## Plots of Seasonal Subseries

### **Germany**
```{r}
data_elec %>% gg_subseries(Germany) +
    ylab("GWt") + xlab("Month") +
    ggtitle("Seasonal subseries plot: Swiss electricity exported to Germany")
``` 

### **France**
```{r}
data_elec %>% gg_subseries(France) +
    ylab("GWt") + xlab("Month") +
    ggtitle("Seasonal subseries plot: Swiss electricity exported to France")
```

### **Italy**
```{r}
data_elec %>% gg_subseries(Italy) +
    ylab("GWt") + xlab("Month") +
    ggtitle("Seasonal subseries plot: Swiss electricity exported to Italy")
```

### **Austria**
```{r}
data_elec %>% gg_subseries(Austria) +
    ylab("GWt") + xlab("Month") +
    ggtitle("Seasonal subseries plot: Swiss electricity exported to Austria")
```

### **Lichtenstein**
```{r}

data_elec %>% gg_subseries(Lichtenstein) +
    ylab("GWt") + xlab("Month") +
    ggtitle("Seasonal subseries plot: Swiss electricity exported to Lichtenstein")
```

### **Total**
```{r}

data_elec %>% gg_subseries(Total) +
    ylab("GWt") + xlab("Month") +
    ggtitle("Seasonal subseries plot: Swiss electricity exported to All countries")
```
