## Project 1: Electricity export

```{r import_data, include=FALSE}
raw_data = read.csv("data/electricity_exports.csv", header = TRUE, fill=TRUE, encoding = "UTF-8")
raw_data = data.frame(raw_data)

```

# Questions 

- Do we need to convert things in the long format to merge all the countries in one column? Maybe not since we are not using any other data


# Data cleaning
We import data and we clean it from <i>NA</i> and from blank rows. We also name the columns. Here is a sample of our data:
```{r data_cleaning, echo=FALSE}
colnames(raw_data) = c('date', 'germany', 'france', 'italy', 'austria', 'lichtenstein', 'total')

#Removing first rows
raw_data = raw_data[-c(1:4),] 

#Selecting columns and removing NAs
clean_data =  select(raw_data, date, germany, france, italy, austria, lichtenstein, total) %>% drop_na() 

#Removing empty rows
clean_data = clean_data[!clean_data$date=="",]

head(clean_data)
```




# Data import 

We directly import the data from the excel file, selecting only the range that contains the data, and then setting the column names accordingly. 

```{r}
#importing data directly from excel
data_elec <- read_excel("data/Electricity export Switzerland.xlsx", 
    range = "A6:G280", col_names = FALSE)

#Setting column names
colnames(data_elec) = c('Date','Germany','France','Italy','Austria','Lichtenstein','Total')
```



# Data cleaning

Looking at the data we see that October is written with a "k", so we change that in the Date column. Then we check for missing values, before proceeding. 

```{r}
# replace "Oktober" with "October" in the Date column
data_elec$Date <- str_replace_all(data_elec$Date, "Oktober", "October")

#This uses the "DataExplorer" package
plot_intro(data_elec)

```

# Converting to tsibble so that we can use the fpp3 and tsibble package functions

```{r}
#Convert to tsibble 
data_elec <- data_elec %>%
  mutate(Date = yearmonth(Date)) %>% #need to do this before converting to get proper format
  as_tsibble(index = Date)

#check that it's a tsibble now, and we can see it recognized the data is monthly because of the [1M] 
is_tsibble(data_elec)
data_elec
```
