# Decomposition

As time series data often consists of different patterns, it is helpful to split time series into components, each representing a pattern category. As a result, we can understand how each element behaves over time and model each separately for greater forecasting accuracy results. It will also help to decide on the type of forecasting model.

For this purpose, we considered different types of decomposition techniques (see Appendix 1.) such us Classical Decomposition, STL Decomposition, and X-11 method. We decided to continue with the second one. 

STL Decomposition is a versatile and robust method that handles any seasonality; seasonal components can change, and smoothness can be controlled. 

We observe strong seasonality and trend patterns in each country and all countries together. The data is non-stationary. 

## STL Decomposition for all countries {.tabset}
### **Germany**
```{r}
data_elec %>%
  model(STL(Germany ~ trend(window = 7) + season(window = "periodic"),
    robust = TRUE)) %>%
  components() %>%
  autoplot()
``` 

### **France**
```{r}
#STL Decomposition_France
data_elec %>%
  model(STL(France ~ trend(window = 7) + season(window = "periodic"),
    robust = TRUE)) %>%
  components() %>%
  autoplot()
```

### **Italy**
```{r}
data_elec %>%
  model(STL(Italy ~ trend(window = 7) + season(window = "periodic"),
    robust = TRUE)) %>%
  components() %>%
  autoplot()
```

### **Austria**
```{r}
data_elec %>%
  model(STL(Austria ~ trend(window = 7) + season(window = "periodic"),
    robust = TRUE)) %>%
  components() %>%
  autoplot()
```

### **Lichtenstein**
```{r}
data_elec %>%
  model(STL(Lichtenstein ~ trend(window = 7) + season(window = "periodic"),
    robust = TRUE)) %>%
  components() %>%
  autoplot()
```

### **Total**
```{r}
data_elec %>%
  model(STL(Total ~ trend(window = 7) + season(window = "periodic"),
    robust = TRUE)) %>%
  components() %>%
  autoplot()

```







