## Decomposition
As time series data often consists of different patterns, it is helpful to split time series into components, each representing a pattern category. As a result, we can understand how each element behaves over time and model each of them separately for greater forecasting accuracy results. 

For this purpose we use different types of decomposition techniques:
* Classical Decomposition assumes seasonal component repeats from year to year which usually is not the case in the reality, over smoothes rapid rises (is not recommended to use, but still...).
* STL Decomposition versatile and robust method, handles any type of seasonality, seasonal component is allowed to change, smootheness can be controlled.
* X-11 method originated in the US Census Bureau and was further developed by Statistics Canada, based on classical decomposition, slightly improved version of classical decomposition, seasonal component is allowed to vary slowly over time, highly robust to outliers and level shifts in the time series.

# Decomposition_Germany
```{r}
#Classical Decomposition_Germany
data_elec %>%
  model(classical_decomposition(Germany, type = "additive")) %>%
  components() %>%
  autoplot() + xlab("Year")

#STL Decomposition_Germany
data_elec %>%
  model(STL(Germany ~ trend(window = 7) + season(window = "periodic"),
    robust = TRUE)) %>%
  components() %>%
  autoplot()

#X-11 method_Germany
x11_dcmp <- data_elec %>%
  model(x11 = X_13ARIMA_SEATS(Germany ~ x11())) %>%
  components()
autoplot(x11_dcmp)

```
# STL Decomposition_France
```{r}
#Classical Decomposition_France
data_elec %>%
  model(classical_decomposition(France, type = "additive")) %>%
  components() %>%
  autoplot() + xlab("Year")

#STL Decomposition_France
data_elec %>%
  model(STL(France ~ trend(window = 7) + season(window = "periodic"),
    robust = TRUE)) %>%
  components() %>%
  autoplot()

#X-11 method_France
x11_dcmp <- data_elec %>%
  model(x11 = X_13ARIMA_SEATS(France ~ x11())) %>%
  components()
autoplot(x11_dcmp)
```
# Decomposition_Italy
```{r}
#Classical Decomposition_Italy
data_elec %>%
  model(classical_decomposition(Italy, type = "additive")) %>%
  components() %>%
  autoplot() + xlab("Year")

#STL Decomposition_Italy
data_elec %>%
  model(STL(Italy ~ trend(window = 7) + season(window = "periodic"),
    robust = TRUE)) %>%
  components() %>%
  autoplot()

#X-11 method_Italy
x11_dcmp <- data_elec %>%
  model(x11 = X_13ARIMA_SEATS(Italy ~ x11())) %>%
  components()
autoplot(x11_dcmp)
```
# Decomposition Austria
```{r}
#Classical Decomposition_Austria
data_elec %>%
  model(classical_decomposition(Austria, type = "additive")) %>%
  components() %>%
  autoplot() + xlab("Year")

#STL Decomposition_Austria
data_elec %>%
  model(STL(Austria ~ trend(window = 7) + season(window = "periodic"),
    robust = TRUE)) %>%
  components() %>%
  autoplot()

#X-11 method_Austria
x11_dcmp <- data_elec %>%
  model(x11 = X_13ARIMA_SEATS(Austria ~ x11())) %>%
  components()
autoplot(x11_dcmp)

```
# Decomposition_Lichtenstein
```{r}
#Classical Decomposition_Lichtenstein
data_elec %>%
  model(classical_decomposition(Lichtenstein, type = "additive")) %>%
  components() %>%
  autoplot() + xlab("Year")

#STL Decomposition_Lichtenstein
data_elec %>%
  model(STL(Lichtenstein ~ trend(window = 7) + season(window = "periodic"),
    robust = TRUE)) %>%
  components() %>%
  autoplot()

#X-11 method_Lichtenstein
x11_dcmp <- data_elec %>%
  model(x11 = X_13ARIMA_SEATS(Lichtenstein ~ x11())) %>%
  components()
autoplot(x11_dcmp)
```
# Decomposition_Total
```{r}
#Classical Decomposition_Total
data_elec %>%
  model(classical_decomposition(Total, type = "additive")) %>%
  components() %>%
  autoplot() + xlab("Year")

#STL Decomposition_Total
data_elec %>%
  model(STL(Total ~ trend(window = 7) + season(window = "periodic"),
    robust = TRUE)) %>%
  components() %>%
  autoplot()

#X-11 method_Total
x11_dcmp <- data_elec %>%
  model(x11 = X_13ARIMA_SEATS(Total ~ x11())) %>%
  components()
autoplot(x11_dcmp)
```

```{r, echo=TRUE, fig.height = 2}
#Seasonality_Germany
data_elec %>% gg_season(Germany, size = 1)

#Seasonality_France
data_elec %>% gg_season(France, size = 1)

#Seasonality_Italy
data_elec %>% gg_season(Italy, size = 1)

#Seasonality_Austria
data_elec %>% gg_season(Austria, size = 1)

#Seasonality_Lichtenstein
data_elec %>% gg_season(Lichtenstein, size = 1)

#Seasonality_Total
data_elec %>% gg_season(Total, size = 1)

```
