
# THINGS THAT NEED TO BE DONE 

In general: 
- Add eda.rmd to appendix 
- Final Forecast Table: replace negative values with 0
- In the forecast we show only the final model chosen, why show lichtenstein 5.5.1 + 5.5.2?

Unit root test:
- Why is the unit root test showing stationarity? 
- Why in unit root take not all of the data? 
- Why convert to tsibble when it's already a tsibble ? 


Country specific:

- Explore huge peak in Austria 2002 -> is it an outlier 
- Explain big drop in Lichtenstein + thought process behind piece-wise model  (Done)
- Should add piece-wise ets if perform better
3.4: STL decomposition analysis :
- Germany 
- France
- Italy
- Austria (Done)
- Lich (Done)
- Total 

3.5 Unit Root Test for Stationarity every countries  (Done)
 
# 1. Introduction 

This project is a forecasting analysis for the electricity exports from Switzerland to several European countries. The data used was all provided by the professor and no additional datasets were used. We have selected the models that fit each country the best (based on some performance metrics) and have created forecasts and CI's for each country as well as the total. In the final report you are now reading, only the most important information is included, and whatever was deemed unnecessary for the report you can find in our code files/appendix. 

The forecasting models used in this project are S-Naive, S-ARIMA, ETS and a variant of ARIMA piece-wise for a specific country. 


# 2. Data Processing 

The data we were given was already cleaned, without any missing values. The only noteworthy cleaning we did, was to format the names of all columns and all rows, and to then convert the final table to a tsibble in order to be able to use functions from the tsibble and fpp3 package. All details on how this was done can be found in the code files.

```{r, echo = FALSE, warning=FALSE, include=FALSE}
#importing data directly from excel
data_elec <- read_excel("data/Electricity export Switzerland.xlsx", 
    range = "A6:G280", col_names = FALSE)

#Setting column names
colnames(data_elec) = c('Date','Germany','France','Italy','Austria','Lichtenstein','Total')

# replace "Oktober" with "October" in the Date column
data_elec$Date <- str_replace_all(data_elec$Date, "Oktober", "October")

#Convert to tsibble 
data_elec <- data_elec %>%
  mutate(Date = yearmonth(Date)) %>% #need to do this before converting to get proper format
  as_tsibble(index = Date)
```



# 3. Exploratory Data Analysis

## 3.1 Historical data plots 

In this section you can find an example of the exploratory analysis we did to identify outliers and behaviors in our data. We created historical plots of all the data for each country, but this is not presented here and can instead be found in our appendix. The anomalies and outliers we discovered in that section, were used to guide our analysis. 

For example, we noticed irregularities in the amplitudes of seasonality over time. For countries like Germany and France, the amplitude of the seasonality seemed to increase towards the most recent years. Based on this, we decided to do a seasonal/trend decomposition for each country to further analyze this.

Furthermore, for Lichtenstein, we noticed a huge drop in exports after 2008-2009, which indicated that we should try different models like the piece-wise model to separate the differences in trend over time. 

## 3.2 Seasonal Sub-series plots 

We also created seasonal sub-series plots to explore specific months in more detail, for each country. Below you can see the one for the total exports: 

```{r}
data_elec %>% gg_subseries(Total) +
    ylab("GWt") + xlab("Month") +
    ggtitle("Seasonal subseries plot: Swiss electricity exported to All countries")
```

Here are some observations based on these plots for each country (which you can find in appendix):  

- Germany: It looks like Germany consistently receives more electricity during the summer months (May, June, July, August). Seasonality seems to vary over time, increasing towards the most recent years.
- France: It looks like there are two peaks in energy exported to France during the year, one in July, and one in December.  
- Italy: Similar energy peak in July.
- Austria: Same trend, with a single peak in the summer months, and then relatively constant energy for the other months.
- Lichtenstein: This country shows the opposite trend, with a very smooth peak in the coldest winter months (Jan,Feb), and the lowest energy exports during the summer months.  
- Total: Clearly seeing the peak in energy exports to countries in the summer, and specifically in July. The other months are at similar levels for the total electricity exports.

In summary, the main observation we got from these historical plots, was that all countries (except Lichtenstein) experience peaks in the electricity they receive from Switzerland in the summer months. 

Before this monthly analysis, we expected that energy exports to these countries, would be higher in the winter months, as that's when people tend to consume more energy to heat up their homes (we assumed this to be one of the biggest drivers in energy consumption). However, in reality it seems like electricity exports are peaking in the summer and not in the winter months. Our explanation for this is that the ways to heat up a home in the winter are mainly based on oil/gas rather than electricity which is why there is no peak for electricity exports in the winter. On the contrary, during the summer months, people tend to cool down their homes using Air-conditioning which primarily uses electricity, hence the peak in the summer months. This does not explain why Lichtenstein does not follow the same pattern, despite being geographically right next to all of these countries (hence having similar climate). 

## 3.3 ACF - Autocorrelation analysis

Before moving on with the models and in order to be able to use them, we wanted to check for autocorrelation in the time series. Here is data on Germany which is lagged by 12 periods:

```{r}
#Graph of 12 lagged months for Germany
data_elec %>% 
  gg_lag(Germany, lags = 1:12, geom="point") + 
  ggtitle("Germany 12-period lag graph")
```

From this graph, we can visualize autocorrelation. It's clear that the autocorrelation is the highest for the 1-month lag, and the 12-month lag. We can see this because the points in the first and last scatterplot (Current month vs Lagged period) approach the 45-degree line, indicating the similarity in magnitude of two the observations. 

Based on the strong and clear presence of autocorrelation, we expect that a model like ARIMA/SARIMA will do a good job to capture this auto-correlation component, and will most likely have the best performance compared to other models. On the contrary, auto-correlation tends to impact the performance of SNAIVE models, as they rely on the assumption that the future values are solely determined by past values without considering any auto-correlation patterns. This suggests that our SNAIVE model will not be fitting the data as well.

## 3.4 STL Decomposition for all countries {.tabset}

We decided to perform an STL decomposition, as it can provide valuable insights and help explore and understand any strange patterns in our data. 

Overall as you can see below, we observed strong seasonality and trend patterns in each country and all countries together which suggested our models should have a way to capture the presence of seasonality and trend. This can be seen in the trend + season_year graphs which show the trend + seasonal component in relation to the overall variation in the data (this is seen using the grey box on the left of each graph). Finally, we can also see that the "remainder" component is quite significant in size (relative to the overall variation) which makes the time series difficult to predict accurately.

### **Germany**
```{r}
data_elec %>%
  model(STL(Germany ~ trend(window = 7) + season(window = "periodic"),
    robust = TRUE)) %>%
  components() %>%
  autoplot()
``` 

### **France**
```{r}
#STL Decomposition_France
data_elec %>%
  model(STL(France ~ trend(window = 7) + season(window = "periodic"),
    robust = TRUE)) %>%
  components() %>%
  autoplot()
```

### **Italy**
```{r}
data_elec %>%
  model(STL(Italy ~ trend(window = 7) + season(window = "periodic"),
    robust = TRUE)) %>%
  components() %>%
  autoplot()
```

### **Austria**
Austria trend undergoes a huge increase during the period 2018-2021, follow by a drastic drop which are not explainable by historical data and strongly suggest that it is affected by a covariate.
Seasonality is constant and stable over time during the whole period.
```{r}
data_elec %>%
  model(STL(Austria ~ trend(window = 7) + season(window = "periodic"),
    robust = TRUE)) %>%
  components() %>%
  autoplot()
```

### **Lichtenstein**
Lichtenstein trend undergoes a drastical drop during the year of 2008, that is not explainable by historical data and strongly suggest that it is affected by a covariate.
Seasonality is constant and stable over time during the whole period. Thus we observe that the amplitude and duration of the seasonal patterns remain unchanged over different time periods.
```{r}
data_elec %>%
  model(STL(Lichtenstein ~ trend(window = 7) + season(window = "periodic"),
    robust = TRUE)) %>%
  components() %>%
  autoplot()
```

### **Total**
```{r}
data_elec %>%
  model(STL(Total ~ trend(window = 7) + season(window = "periodic"),
    robust = TRUE)) %>%
  components() %>%
  autoplot()

```

## 3.5 Unit Root Test for Stationarity {.tabset}

In the final part of our EDA, we wanted to confirm our suspicion of the presence of non-stationarity (since we found a significant trend and seasonal component in the STL analysis). To do this, we used the Unit Root Test to check for the presence of a unit root in the time series, which is an indication of non-stationarity. Below are the null and alternative hypotheses for this statistical test: 

$$H_0: The\ time\ series\ has\ a\ unit\ root\ (non\ stationary)\\ H_1: The\ time\ series\ is\ stationary$$

After doing the test for all countries, we found that all of the time series are stationary at a significance level of: `alpha = 0.05`.


### **Germany**
The test statistic was -6.0768. The p-value of the test was 0.01, which indicates strong evidence to reject the null hypothesis of non-stationarity at `alpha = 0.05`. Thus Germany data is a stationary time series.
```{r, warning=FALSE, echo=FALSE}
# Load the required package
library(tseries)


G_since_2000 <- data_elec %>% select(Date,Germany) #%>% filter(Date >= as.Date("2010-01-01"))
ts_g<- ts(G_since_2000$Germany, frequency=12, start=c(2000,1))

# Check for linearity using ADF test
adf.test(ts_g)
```
### **France**
The test statistic was -4.6123 The p-value of the test was 0.01, which indicates strong evidence to reject the null hypothesis of non-stationarity at `alpha = 0.05`. Thus France data is a stationary time series.
```{r, warning=FALSE, echo=FALSE}


F_since_2000 <- data_elec %>% select(Date,France) %>% filter(Date >= as.Date("2000-01-01"))
ts_F<- ts(F_since_2000$France, frequency=12, start=c(2000,1))

# Check for linearity using ADF test
adf.test(ts_F)
```
### **Italy**
The test statistic was -6.8897 The p-value of the test was 0.01. Thus Italy data is a stationary time series.
```{r, warning=FALSE, echo=FALSE}


I_since_2000 <- data_elec %>% select(Date,Italy) %>% filter(Date >= as.Date("2000-01-01"))
ts_I<- ts(I_since_2000$Italy, frequency=12, start=c(2000,1))

# Check for linearity using ADF test
adf.test(ts_I)
```
### **Austria**
The test statistic was -3.7273 The p-value of the test was 0.02443, which indicates strong evidence to reject the null hypothesis of non-stationarity at `alpha = 0.05`. Thus Austria data is a stationary time series.
```{r, warning=FALSE, echo=FALSE}


A_since_2000 <- data_elec %>% select(Date,Austria) %>% filter(Date >= as.Date("2000-01-01"))
ts_A<- ts(A_since_2000$Austria, frequency=12, start=c(2000,1))

# Check for linearity using ADF test
adf.test(ts_A)
```
### **Lichtenstein**
The test statistic was -6.5052 The p-value of the test was 0.01. Thus Lichtenstein data is a stationary time series.
```{r, warning=FALSE, echo=FALSE}

Lichtenstein_since_2000 <- data_elec %>% select(Date,Lichtenstein) %>% filter(Date >= as.Date("2000-01-01"))
ts_Lich <- ts(Lichtenstein_since_2000$Lichtenstein, frequency=12, start=c(2000,1))

# Check for linearity using ADF test
adf.test(ts_Lich)
```

### **Total**
Finally, The test statistic was -4.0009 The p-value of the test was 0.01103. Thus Total data is a stationary time series.
```{r, warning=FALSE, echo=FALSE}


Tot_since_2000 <- data_elec %>% select(Date,Total) %>% filter(Date >= as.Date("2000-01-01"))
ts_Tot<- ts(Tot_since_2000$Total, frequency=12, start=c(2000,1))

# Check for linearity using ADF test
adf.test(ts_Tot)
```