# 5. Forecast

For each of our country forecasts, we have decided to use the model with the lowest RMSE as shown in the previous section. This is because we want our models to be as "accurate" as possible, in away that minimizes the error/distance between our forecast values and the actual values.

Below, for each country, you can see a residual analysis for every selected model, a graph of the forecast, and finally the forecast table. The outcome of the residual analysis is to confirm that the model has done a good job fitting the data, and more specifically, here's what we obtained from it: 

A good model fit has the following characteristics in terms of its residuals:

- The residuals are distributed symmetrically, in a shape that resembles a Normal distribution. 
- Low ACF (autocorrelation) in the first few lags. 
- No Heteroskedasticity: the variance of the residuals is constant. 
- There is no trend in the residuals. 

In essence, what this all means, is that the residuals are white noise. Let's now look at the results for each country, and make some more specific comments: 

## 5.1 Germany{.tabset}
We fit Germany electricity demand data using the ETS model.
```{r, warning=FALSE}
# Modelling ARIMA automatically
ets_germany <- data_elec %>%
  select(Germany) %>%
  model(ets = ETS(Germany))

# Forecasting using the models
forecast_ets_germany <- ets_germany %>% forecast(h = 13) %>% hilo(90)
```

### **Checking Residuals**
The output below suggests that the ETS model did a decent job in capturing all the dynamics in data, as the residuals seem to be white noise.

However, it seems like this model for Germany is not fitting well. More specifically, we see that there is more variation in the distribution of the residuals of Germany's model. Nevertheless, the distribution of the errors is symmetric, which is good. Furthermore, we notice the peaks in some of the lagged periods of the ACF graph, indicating the presence of autocorrelation between the time periods and the previous time periods, which is not great in terms of how well the model fits the data. 
```{r}
ets_germany %>% gg_tsresiduals(lag_max = 36) + labs(title = "ETS Germany residuals analysis")
```

### **Graphing the forecast**
For better visualization, we plot our forecast results starting from 2015.
```{r}
ets_germany %>% forecast(h = 13) %>% autoplot(Germany_since_2015) +
  labs(title = "ETS Forecast for Germany")

#Extracting the forecasted values
forecast_table_germany_e <- data.frame(Model = c("ETS"),
                              Forecast_Values = c(forecast_ets_germany))



forecast_table_germany_e <- forecast_table_germany_e %>% select(Forecast_Values.Date,Forecast_Values..mean, Forecast_Values.90.) 
forecast_table_germany_e$Country <- "Germany"

colnames(forecast_table_germany_e)[1] <- "Month"
colnames(forecast_table_germany_e)[2] <- "PF"
colnames(forecast_table_germany_e)[3] <- "CI"


```
### **Forecast Table**
The resulting forecast table for Germany is shown below. 
```{r}
#forecast_table_germany_e
kbl(forecast_table_germany_e) %>%
  kable_styling(fixed_thead = T)
```

## 5.2 Italy{.tabset}
We fit Italy electricity demand data using the ARIMA model.
```{r}
# Modelling ETS automatically
arima_italy <- data_elec %>%
  select(Italy) %>%
  model(ARIMA(Italy))

# Forecasting using the models
forecast_arima_italy <- arima_italy %>% forecast(h = 13) %>% hilo(90)
```

### **Checking Residuals**
The output below suggests that the ARIMA model did well in capturing all the dynamics in data, as the residuals seem to be white noise.
```{r}
arima_italy %>% gg_tsresiduals(lag_max = 36) + labs(title = "ARIMA Italy residuals analysis")
```

### **Graphing the forecast**
For better visualization, we plot our forecast results starting from 2018.
```{r}
arima_italy %>% forecast(h = 13) %>% autoplot(Italy_since_2018) +
  labs(title = "ARIMA Forecast for Italy")

#Extracting the forecasted values
forecast_table_italy_a <- data.frame(Model = c("ARIMA"),
                          Forecast_Values = c(forecast_arima_italy))

forecast_table_italy_a <- forecast_table_italy_a %>% select(Forecast_Values.Date,Forecast_Values..mean, Forecast_Values.90.)
forecast_table_italy_a$Country <- "Italy"

colnames(forecast_table_italy_a)[1] <- "Month"
colnames(forecast_table_italy_a)[2] <- "PF"
colnames(forecast_table_italy_a)[3] <- "CI"
```

### **Forecast Table**
The resulting forecast table for Italy is shown below. 
```{r}
#forecast_table_italy_a
kbl(forecast_table_italy_a) %>%
  kable_styling(fixed_thead = T)
```

## 5.3 Austria{.tabset}
We fit Austria electricity demand data using the ETS model.
```{r}
# Modelling ETS automatically
ets_austria <- data_elec %>%
  select(Austria) %>%
  model(ETS(Austria))

# Forecasting using the models
forecast_ets_austria <- ets_austria %>% forecast(h = 13) %>% hilo(90)
```

### **Checking Residuals**
The output below suggests that the ETS model did well in capturing all the dynamics in data, as the residuals seem to be white noise.
```{r}
ets_austria %>% gg_tsresiduals(lag_max = 36) + labs(title = "ETS Austria residuals analysis")
```

### **Graphing the forecast**
For better visualization, we plot our forecast results starting from 2018.
```{r}
ets_austria %>% forecast(h = 13) %>% autoplot(Austria_since_2018) +
  labs(title = "ETS Forecast for Austria")

#Extracting the forecasted values
forecast_table_austria_e <- data.frame(Model = c("ETS"),
                          Forecast_Values = c(forecast_ets_austria))

forecast_table_austria_e <- forecast_table_austria_e %>% select(Forecast_Values.Date,Forecast_Values..mean, Forecast_Values.90.)
forecast_table_austria_e$Country <- "Austria"

colnames(forecast_table_austria_e)[1] <- "Month"
colnames(forecast_table_austria_e)[2] <- "PF"
colnames(forecast_table_austria_e)[3] <- "CI"
```

### **Forecast Table**
The resulting forecast table for Austria is shown below. 
```{r}
#forecast_table_austria_e
kbl(forecast_table_austria_e) %>%
  kable_styling(fixed_thead = T)

```

## 5.4 France{.tabset}
We fit France electricity demand data using the ETS model.
```{r}
# Modelling ETS automatically
ets_france <- data_elec %>%
  select(France) %>%
  model(ETS(France))

# Forecasting using the models
forecast_ets_france <- ets_france %>% forecast(h = 13) %>% hilo(90)
```

### **Checking Residuals**
The output below suggests that the ETS model did a decent job in capturing all the dynamics in data, as the residuals seem to be white noise.

However, it seems like this model for France is not fitting as well as the other models for the previous countries. More specifically, we see that there is more variation in the distribution of the residuals of France's model compared to other countries. Nevertheless, the distribution of the errors is symmetric, which is good. Furthermore, we notice a peak in the first lagged period of the ACF graph, indicating the presence of autocorrelation between a time period and the previous time period, which is not great in terms of how well the model fits the data. 

```{r}
ets_france %>% gg_tsresiduals(lag_max = 36) + labs(title = "ETS France residuals analysis")
```

### **Graphing the forecast**
For better visualization, we plot our forecast results starting from 2015.
```{r}
ets_france %>% forecast(h = 13) %>% autoplot(France_since_2015) +
  labs(title = "ETS Forecast for France")

#Extracting the forecasted values
forecast_table_france_e <- data.frame(Model = c("ETS"),
                          Forecast_Values = c(forecast_ets_france))

forecast_table_france_e <- forecast_table_france_e %>% select(Forecast_Values.Date,Forecast_Values..mean, Forecast_Values.90.)
forecast_table_france_e$Country <- "France"

colnames(forecast_table_france_e)[1] <- "Month"
colnames(forecast_table_france_e)[2] <- "PF"
colnames(forecast_table_france_e)[3] <- "CI"

```

### **Forecast Table**
The resulting forecast table for France is shown below. 
```{r}
#forecast_table_france_e
kbl(forecast_table_france_e) %>%
  kable_styling(fixed_thead = T)

```

## 5.5.1 Lichtenstein{.tabset}

We fit Lichtenstein electricity demand data using the ETS model.

```{r, warning=FALSE, echo=FALSE}
# Modelling ETS automatically
ets_Licht <- data_elec %>%
  select(Lichtenstein) %>%
  model(ETS(Lichtenstein))
# Getting the Accuracy scores for models
#report(ets_Licht)

# Forecasting using the models
forecast_ets_Licht <- ets_Licht %>% forecast(h = 13) %>% hilo(90)
forecast_ets_Licht$.mean <- ifelse(forecast_ets_Licht$.mean < 0, 0, forecast_ets_Licht$.mean)
```

### **Checking Residuals**
```{r}
#Checking the residuals before forecasting
ets_Licht %>% gg_tsresiduals(lag_max = 36) + labs(title = "ETS Lichtenstein residuals analysis")
```

### **Graphing the forecast**

```{r}
# Graphing the forecast
ets_Licht %>% forecast(h = 13) %>% autoplot(Lichtenstein_after_2008) +
  labs(title = "ETS Forecast for Lichtenstein")

#Extracting the forecasted values
forecast_table_Lichtenstein_ets <- data.frame(Model = c("ETS"),
                              Forecast_Values = c(forecast_ets_Licht))

forecast_table_Lichtenstein_ets <- forecast_table_Lichtenstein_ets %>% select(Forecast_Values.Date,Forecast_Values..mean, Forecast_Values.90.)
forecast_table_Lichtenstein_ets$Country <- "Lichtenstein"

colnames(forecast_table_Lichtenstein_ets)[1] <- "Month"
colnames(forecast_table_Lichtenstein_ets)[2] <- "PF"
colnames(forecast_table_Lichtenstein_ets)[3] <- "CI"
```
### **Forecast Table**
The resulting forecast table for Lichtenstein is shown below. 
```{r}
#forecast_table_Lichtenstein_ets
kbl(forecast_table_Lichtenstein_ets) %>%
  kable_styling(fixed_thead = T)
```

## 5.5.2 Lichtenstein{.tabset}

We fit Lichtenstein electricity demand data using the SNaive model.

```{r, warning=FALSE, echo=FALSE}
# Modelling SNaive automatically
n_Licht <- data_elec %>%
  select(Lichtenstein) %>%
  model(SNAIVE(Lichtenstein))
# Getting the Accuracy scores for models
#report(n_Licht)

# Forecasting using the models
forecast_n_Licht <- n_Licht %>% forecast(h = 13) %>% hilo(90)
forecast_n_Licht$.mean <- ifelse(forecast_n_Licht$.mean < 0, 0, forecast_n_Licht$.mean)
```

### **Checking Residuals**
As expected the SNaive is a relatively simple model, it hardly capture all the dynamics in data, since the residuals are not white noise. Also, it is not surprising to observe correlation between ts and lags, since it is inherent from a Naive models.

```{r, warning=FALSE}
#Checking the residuals before forecasting
n_Licht %>% gg_tsresiduals(lag_max = 36) + labs(title = "SNaive Lichtenstein residuals analysis")
```

### **Graphing the forecast**

```{r}
# Graphing the forecast
n_Licht %>% forecast(h = 13) %>% autoplot(Lichtenstein_after_2008) +
  labs(title = "SNaive Forecast for Lichtenstein")

#Extracting the forecasted values
forecast_table_Lichtenstein_n <- data.frame(Model = c("SNaive"),
                              Forecast_Values = c(forecast_n_Licht))

forecast_table_Lichtenstein_n <- forecast_table_Lichtenstein_n %>% select(Forecast_Values.Date,Forecast_Values..mean, Forecast_Values.90.)
forecast_table_Lichtenstein_n$Country <- "Lichtenstein"

colnames(forecast_table_Lichtenstein_n)[1] <- "Month"
colnames(forecast_table_Lichtenstein_n)[2] <- "PF"
colnames(forecast_table_Lichtenstein_n)[3] <- "CI"


#### TRY TO ADJUST THE CONFIDENCE INTERVAL BY DOING SO::

# Adjusting the lower bound of the 90% confidence interval
lower_str <- gsub("\\[(.*),.*\\]90", "\\1", forecast_table_Lichtenstein_n$CI)
upper_str <- gsub("\\[.*, (.*)\\]90", "\\1", forecast_table_Lichtenstein_n$CI)
ci_str <- gsub("\\[.*\\](90)", "\\1", forecast_table_Lichtenstein_n$CI)

# Converting to numeric values
lower_bound <- as.numeric(lower_str)
upper_bound <- as.numeric(upper_str)
ci <- as.numeric(ci_str)

# Adjusting the lower bound and CI
lower_bound <- pmax(lower_bound, 0)
adjusted_ci <- upper_bound - lower_bound

# Creating the data frame
output_df_lich <- data.frame("Lower Bound" = lower_bound,
                        "Upper Bound" = upper_bound,
                        "CI" = adjusted_ci)

# Printing the adjusted output
print(output_df_lich)

```
### **Forecast Table**
The resulting forecast table for Lichtenstein is shown below. 
```{r}
#forecast_table_Lichtenstein_n
kbl(forecast_table_Lichtenstein_n) %>%
  kable_styling(fixed_thead = T)
```

## 5.6 Total{.tabset}
We fit Total electricity demand data using the ARIMA model.
```{r}
# Modelling ETS automatically
arima_total <- data_elec %>%
  select(Total) %>%
  model(ARIMA(Total))

# Forecasting using the models
forecast_arima_total <- arima_total %>% forecast(h = 13) %>% hilo(90)
```

### **Checking Residuals**
The output below suggests that the ARIMA model did well in capturing all the dynamics in data, as the residuals seem to be white noise.
```{r}
arima_total %>% gg_tsresiduals(lag_max = 36) + labs(title = "ARIMA residuals analysis for all countries")

```

### **Graphing the forecast**
For better visualization, we plot our forecast results starting from 2015.
```{r}
arima_total %>% forecast(h = 13) %>% autoplot(Total_since_2015) +
  labs(title = "ARIMA Forecast for All Countries")

#Extracting the forecasted values
forecast_table_total_a<- data.frame(Model = c("ARIMA"),
                          Forecast_Values = c(forecast_arima_total))

forecast_table_total_a <- forecast_table_total_a %>% select(Forecast_Values.Date,Forecast_Values..mean, Forecast_Values.90.)
forecast_table_total_a$Country <- "Total"

colnames(forecast_table_total_a)[1] <- "Month"
colnames(forecast_table_total_a)[2] <- "PF"
colnames(forecast_table_total_a)[3] <- "CI"

```

### **Forecast Table**
The resulting forecast table for Total is shown below. 
```{r}
#forecast_table_total_a
kbl(forecast_table_total_a) %>%
  kable_styling(fixed_thead = T)
```


## Combining all forecasts into one table: 
Below is the final table containing `Month,` point forecast `PF,` 90% lower and upper confidence levels interval forecast `CI,` and `Country.`  
```{r, warning=FALSE}

final_fc <- bind_rows(forecast_table_germany_e, forecast_table_italy_a, forecast_table_france_e, forecast_table_austria_e,forecast_table_Lichtenstein_n, forecast_table_total_a)

#Rounding all values to 0 significant figures because at the moment they have 4 decimals each...
final_fc$PF <- round(final_fc$PF)
final_fc$CI <- round(final_fc$CI)

#Removing all non-negative values from the CI column and replacing them by 0 - With string manipulation bc i can't find another way
final_fc$CI <- str_replace(final_fc$CI, "\\[(-\\d+),", "[0,")

kbl(cbind(final_fc)) %>%
  kable_paper() %>%
  scroll_box(width = "100%", height = "500px")

#str(final_fc)
```

# 6. Challenges and Further Analysis

In this section we will comment on things didn't go so well in our analysis, and things that could be improved. 

Firstly, in the confidence bounds, some of Germany's, Lichtenstein's and Austria's lower bound values were negative at the 90% confidence intervals, which you can actually see in the graphs of the forecasts for each country. This was a problem because electricity exports can't physically be negative, and the lowest value they can take is zero. This happened because when fitting the models, we didn't specify that the forecasts shouldn't take negative values, and obviously the models can't know that themselves. To solve this issue, we decided to manually set the lower bounds of these confidence intervals to 0 as it wouldn't make any sense for them to be negative, however we do have to mention that by doing so, the confidence intervals we show are not 90% intervals. 

Secondly, we decided not to add any covariates to our models, and only use the historical data we were given. Covariates could potentially help our forecasts be more accurate, as they can capture patterns and the effects of external factors which have an impact on electricity demand. An example of such a factor could be monthly average temperature values, because temperature probably plays a big role in energy consumption at the national level. Another example of a factor we could have included in our analysis would be the average hours of sunlight, because people tend to use more energy to light up their house in the winter compared to the summer. Another factor could be the implementation and use of different forms of energy, such as wind energy/nuclear energy to supply power inside a country, rather than simply importing it from Switzerland.
