# Forecast

## Germany{.tabset}

```{r}
# Modelling ARIMA automatically
arima_germany <- data_elec %>%
  select(Germany) %>%
  model(arima = ARIMA(Germany))

# Forecasting using the models
forecast_arima_germany <- arima_germany %>% forecast(h = 13, level = 90)
```

### **Checking Residuals**
```{r}
arima_germany %>% gg_tsresiduals(lag_max = 36) + labs(title = "SARIMA Germany residuals analysis")
```

### **Graphing the forecast**
```{r}
arima_germany %>% forecast(h = 13) %>% autoplot(Germany_since_2015) +
  labs(title = "ARIMA Forecast for Germany")

#Extracting the forecasted values
forecast_table_germany_a <- data.frame(Model = c("ARIMA"),
                              Forecast_Values = c(forecast_arima_germany))


forecast_table_germany_a <- forecast_table_germany_a %>% select(Forecast_Values.Date,Forecast_Values..mean)

colnames(forecast_table_germany_a)[1] <- "Month"
colnames(forecast_table_germany_a)[2] <- "Germany ARIMA"
```

### **Forecast Table**
```{r}
forecast_table_germany_a

```

## Italy{.tabset}

```{r}
# Modelling ARIMA automatically
arima_italy <- data_elec %>%
  select(Italy) %>%
  model(arima = ARIMA(Italy))

# Forecasting using the models
forecast_arima_italy <- arima_italy %>% forecast(h = 13)
```

### **Checking Residuals**
```{r}
arima_italy %>% gg_tsresiduals(lag_max = 36) + labs(title = "SARIMA Italy residuals analysis")
```

### **Graphing the forecast**
```{r}
arima_italy %>% forecast(h = 13) %>% autoplot(Italy_since_2018) +
  labs(title = "ARIMA Forecast for Italy")

#Extracting the forecasted values
forecast_table_italy_a <- data.frame(Model = c("ARIMA"),
                          Forecast_Values = c(forecast_arima_italy))

forecast_table_italy_a <- forecast_table_italy_a %>% select(Forecast_Values.Date,Forecast_Values..mean)

colnames(forecast_table_italy_a)[1] <- "Month"
colnames(forecast_table_italy_a)[2] <- "Italy ARIMA"
```

### **Forecast Table**
```{r}
forecast_table_italy_a
```

## Austria{.tabset}
```{r}
# Modelling ARIMA automatically
arima_austria <- data_elec %>%
  select(Austria) %>%
  model(arima = ARIMA(Austria))

# Forecasting using the models
forecast_arima_austria <- arima_austria %>% forecast(h = 13)
```

### **Checking Residuals**
```{r}
arima_austria %>% gg_tsresiduals(lag_max = 36) + labs(title = "SARIMA Austria residuals analysis")
```

### **Graphing the forecast**
```{r}
arima_austria %>% forecast(h = 13) %>% autoplot(Austria_since_2015) +
  labs(title = "ARIMA Forecast for Austria")

#Extracting the forecasted values
forecast_table_austria_a <- data.frame(Model = c("ARIMA"),
                              Forecast_Values = c(forecast_arima_austria))

forecast_table_austria_a <- forecast_table_austria_a %>% select(Forecast_Values.Date,Forecast_Values..mean)

colnames(forecast_table_austria_a)[1] <- "Month"
colnames(forecast_table_austria_a)[2] <- "Austria ARIMA"
```

### **Forecast Table**
```{r}
forecast_table_austria_a

```

## France{.tabset}
```{r}
# Modelling ARIMA automatically
arima_france <- data_elec %>%
  select(France) %>%
  model(arima = ARIMA(France))

# Forecasting using the models
forecast_arima_france <- arima_france %>% forecast(h = 13)
```

### **Checking Residuals**
```{r}
arima_france %>% gg_tsresiduals(lag_max = 36) + labs(title = "SARIMA France residuals analysis")
```

### **Graphing the forecast**
```{r}
# Graphing the forecast
arima_france %>% forecast(h = 13) %>% autoplot(France_since_2015) +
  labs(title = "ARIMA Forecast for France")

#Extracting the forecasted values
forecast_table_france_a <- data.frame(Model = c("ARIMA"),
                              Forecast_Values = c(forecast_arima_france))

forecast_table_france_a <- forecast_table_france_a %>% select(Forecast_Values.Date,Forecast_Values..mean)

colnames(forecast_table_france_a)[1] <- "Month"
colnames(forecast_table_france_a)[2] <- "France ARIMA"

```

### **Forecast Table**
```{r}
forecast_table_france_a

```


## Total{.tabset}
```{r}
# Modelling ARIMA automatically
arima_total <- data_elec %>%
  select(Total) %>%
  model(arima = ARIMA(Total))

# Forecasting using the models
forecast_arima_total <- arima_total %>% forecast(h = 13)
```

### **Checking Residuals**
```{r}
arima_total %>% gg_tsresiduals(lag_max = 36) + labs(title = "SARIMA residuals analysis for all countries")

```

### **Graphing the forecast**
```{r}
# Graphing the forecast
arima_total %>% forecast(h = 13) %>% autoplot(Total_since_2015) +
  labs(title = "ARIMA Forecast for all countries")

#Extracting the forecasted values
forecast_table_total_a <- data.frame(Model = c("ARIMA"),
                              Forecast_Values = c(forecast_arima_total))

forecast_table_total_a <- forecast_table_total_a %>% select(Forecast_Values.Date,Forecast_Values..mean)

colnames(forecast_table_total_a)[1] <- "Month"
colnames(forecast_table_total_a)[2] <- "Total ARIMA"

```

### **Forecast Table**
```{r}
forecast_table_total_a
```


## Combining all forecasts into one table: 

```{r}

final_fc <- left_join(forecast_table_total_a,forecast_table_germany_a, by = "Month")
final_fc <- final_fc %>% left_join(forecast_table_france_a, by = "Month")
final_fc <- final_fc %>% left_join(forecast_table_italy_a, by = "Month")
final_fc <- final_fc %>% left_join(forecast_table_austria_a, by = "Month")
#final_fc <- final_fc %>% left_join(forecast_table_Lichtenstein_a, by = "Month")


```

