
## Total{.tabset}

```{r}
Total_since_2015 <- data_elec %>% select(Date,Total) %>% filter(Date >= as.Date("2015-01-01"))
```
### **Testing Models**
Below is the plot of how well each model fits the data based on a 60-period prediction starting from 2016. 
```{r}

#Split the data
training_tot <- data_elec %>% select(Date, Total) %>%  filter(Date < as.Date("2016-01-01"))
test_tot <- data_elec %>% select(Date, Total) %>% filter(Date >= as.Date("2016-01-01"))

# Fit ARIMA model and generate forecasts
data_fit_tot_a <- training_tot %>%
  model(ARIMA(Total))
forecasts_tot_a <- data_fit_tot_a %>%
  forecast(h = 60)

# Fit ETS model and generate forecasts
data_fit_tot_e <- training_tot %>%
  model(ETS(Total))
forecasts_tot_e <- data_fit_tot_e %>%
  forecast(h = 60)

# Fit seasonal naive model and generate forecasts
data_fit_tot_n <- training_tot %>%
  model(SNAIVE(Total))
forecasts_tot_n <- data_fit_tot_n %>%
  forecast(h = 60)

# Combine forecasts into a single data frame
all_forecasts_tot <- bind_rows(
  data.frame(Date = forecasts_tot_a$Date, Method = "ARIMA", Forecast = forecasts_tot_a$.mean),
  data.frame(Date = forecasts_tot_e$Date, Method = "ETS", Forecast = forecasts_tot_e$.mean),
  data.frame(Date = forecasts_tot_n$Date, Method = "SNAIVE", Forecast = forecasts_tot_n$.mean))


# Plot all three sets of forecasts together
data_elec %>% autoplot(Total) +
  geom_line(data = all_forecasts_tot, aes(x = Date, y = Forecast, color = Method)) +
  labs(title = "Electricity Demand to all countries")

```

### **Measuring Model Accuracy**
According to the accuracy table below, RMSE, MAE, and other indicators, ETS has the lowest values on the test data. However, ARIMA has lower values of AIC=2683.45, AICc=2683.9, and BIC=2702.99 than the ETS model. 
```{r}
#Accuracy
total_accuracy_a <-data_fit_tot_a %>%
  refit(test_tot) %>%
  accuracy()

total_accuracy_e <-data_fit_tot_e %>%
  refit(test_tot) %>%
  accuracy()

total_accuracy_n <-data_fit_tot_n %>%
  refit(test_tot) %>%
  accuracy()

total_accuracy_table <- rbind(
  data.frame(total_accuracy_a),
  data.frame(total_accuracy_e),
  data.frame(total_accuracy_n))



#AIC
report(data_fit_tot_a)
total_accuracy_table
report(data_fit_tot_e)

```


### **Residuals**
The output below also suggests that the ARIMA model did well in capturing all the dynamics in data, as the residuals seem to be white noise.
```{r}
gg_tsresiduals(data_fit_tot_a) + labs(title = "ARIMA Total residuals analysis")

gg_tsresiduals(data_fit_tot_e) + labs(title = "ETS Total residuals analysis")

gg_tsresiduals(data_fit_tot_n) + labs(title = "SNAIVE Total residuals analysis")
```



## Result
All of these metrics are important for evaluating forecast accuracy. Still, we decided to give more weight to AIC, as this indicator considers both the complexity and the model's fit. As a result, the ARIMA model is selected to forecast the electricity demand in Germany, Italy, Austria, France, and for all countries together.




















