# 4. Model Selection

## Methodology
Before creating forecasts, we wanted to discover which model fits our data the best. To evaluate this, we have decided to fit different models for each country, and then pick the best one.

To do this, we split our data into a training and a test set. The first one we will use to estimate any parameters of the forecasting model, and the second is to examine each model's accuracy. The training set for all countries is basically a long time period, from the beginning of our data until the end of 2015, and then the rest of the data is used in the test set. 

The different models we decided to explore are S-ARIMA, ETS and S-NAIVE, and we used them to forecast 60 periods (months) and then compare those with the data in the test set. 

Models automatically select the optimal parameters by searching through different combinations and selecting the best model based on a predefined criterion. We don't specify their parameters manually.

For each country, we selected the model with the best accuracy metrics, as we will explain below. Some of the metrics we will look at are RMSE and MAE and low metric values indicate a better predictive performance of the model. A value of 0 indicates a perfect fit between the predicted and actual values. 
Residuals analysis is also going to be plotted to see how well the model captures the dynamics of the data. Good models' residuals should be stationary (white noise) and have no patterns. 

As the most accurate forecast is of interest, we will give more weight to the model with low values of RMSE and MAE, even though another model has a higher AIC (see Appendix 2.).

## 4.1 Germany{.tabset}

```{r}

Germany_since_2015 <- data_elec %>% 
  select(Date,Germany) %>% 
  suppressWarnings(filter(Date >= as.Date("2015-01-01")))
```

### **Testing Models**
Below is the plot of how well each model fits the data based on a 60-period prediction starting from 2016. 
```{r, warning=FALSE}

#Split the data
training_ge <- data_elec %>% select(Date,Germany) %>% filter(Date < as.Date("2016-01-01"))
test_ge <- data_elec %>% select(Date,Germany) %>% filter(Date >= as.Date("2016-01-01"))
```

```{r}
# Fit ARIMA model and generate forecasts
data_fit_ge_a <- training_ge %>%
  model(ARIMA(Germany))
forecasts_ge_a <- data_fit_ge_a %>%
  forecast(h = 60)

# Fit ETS model and generate forecasts
data_fit_ge_e <- training_ge %>%
  model(ETS(Germany))
forecasts_ge_e <- data_fit_ge_e %>%
  forecast(h = 60)

# Fit seasonal naive model and generate forecasts
data_fit_ge_n <- training_ge %>%
  model(SNAIVE(Germany))
forecasts_ge_n <- data_fit_ge_n %>%
  forecast(h = 60)

# Combine forecasts into a single data frame
all_forecasts_ge <- bind_rows(
  data.frame(Date = forecasts_ge_a$Date, Method = "ARIMA", Forecast = forecasts_ge_a$.mean),
  data.frame(Date = forecasts_ge_e$Date, Method = "ETS", Forecast = forecasts_ge_e$.mean),
  data.frame(Date = forecasts_ge_n$Date, Method = "SNAIVE", Forecast = forecasts_ge_n$.mean))


# Plot all three sets of forecasts together
data_elec %>% autoplot(Germany)  +
  geom_line(data = all_forecasts_ge, aes(x = Date, y = Forecast, color = Method)) +
  labs(title = "Electricity Consumption in Germany")

```


### **Measuring Model Accuracy**
According to the accuracy table RMSE, MAE and other indicators, ETS has the lowest values on the test data. 
The ARIMA model has an AIC of AIC=2260.11, AICc of AICc=2260.6, and BIC of 2279.27. On the other hand, the ETS model has an AIC of 2797.057, AICc of 2799.784, and BIC of 2845.919. Therefore, based on these criteria, we can conclude that the ARIMA model fits the data better than the ETS model.

```{r}
#Accuracy
germany_accuracy_a <- accuracy(forecasts_ge_a, test_ge)

germany_accuracy_e <- accuracy(forecasts_ge_e, test_ge)

germany_accuracy_n <- accuracy(forecasts_ge_n, test_ge)

germany_accuracy_table <- rbind(
  data.frame(germany_accuracy_a),
  data.frame(germany_accuracy_e),
  data.frame(germany_accuracy_n))



```

```{r, warning=FALSE, echo=FALSE}
germany_accuracy_table[ 1:3,1:10] %>%
  kbl() %>%
  kable_paper(full_width = F) %>%
  column_spec(4, color = "white",
              background = spec_color(germany_accuracy_table$RMSE[1:4],end = 0.6)) %>%
    column_spec(5, color = "white",
              background = spec_color(germany_accuracy_table$MAE[1:4],end = 0.6))
```

```{r, warning=FALSE}

#AIC
report(data_fit_ge_a)
report(data_fit_ge_e)

```

### **Residuals**
The output below also suggests that the ARIMA model did well in capturing all the dynamics in data, as the residuals seem to be white noise.
```{r}
gg_tsresiduals(data_fit_ge_a) + labs(title = "ARIMA Germany residuals analysis")

gg_tsresiduals(data_fit_ge_e) + labs(title = "ETS Germany residuals analysis")

gg_tsresiduals(data_fit_ge_n) + labs(title = "SNAIVE Germany residuals analysis")
```




















