
## 4.2 Italy{.tabset}

```{r, warning=FALSE}
#Selecting Italy only since 2018 to better display the forecast. 2018 will both show the trend BEFORE covid + improve display 
Italy_since_2018 <- data_elec %>% select(Date,Italy) %>% filter(Date >= as.Date("2018-01-01"))
```

### **Testing Models**
Below is the plot of how well each model fits the data based on a 60-period prediction starting from 2016. 
```{r, warning=FALSE}

#Split the data
training_it <- data_elec %>% select(Date, Italy) %>%  filter(Date < as.Date("2016-01-01"))
test_it <- data_elec %>% select(Date, Italy) %>% filter(Date >= as.Date("2016-01-01"))

# Fit ARIMA model and generate forecasts
data_fit_it_a <- training_it %>%
  model(ARIMA(Italy)) 
forecasts_it_a <- data_fit_it_a %>%
  forecast(h = 60)


# Fit ETS model and generate forecasts
data_fit_it_e <- training_it %>%
  model(ETS(Italy))
forecasts_it_e <- data_fit_it_e %>%
  forecast(h = 60)

# Fit seasonal naive model and generate forecasts
data_fit_it_n <- training_it %>%
  model(SNAIVE(Italy))
forecasts_it_n <- data_fit_it_n %>%
  forecast(h = 60)

# Combine forecasts into a single data frame
all_forecasts_it <- bind_rows(
  data.frame(Date = forecasts_it_a$Date, Method = "ARIMA", Forecast = forecasts_it_a$.mean),
  data.frame(Date = forecasts_it_e$Date, Method = "ETS", Forecast = forecasts_it_e$.mean),
  data.frame(Date = forecasts_it_n$Date, Method = "SNAIVE", Forecast = forecasts_it_n$.mean))


# Plot all three sets of forecasts together
data_elec %>% autoplot(Italy) +
  geom_line(data = all_forecasts_it, aes(x = Date, y = Forecast, color = Method)) +
  labs(title = "Electricity Demand in Italy")

```

### **Measuring Model Accuracy**
According to the accuracy table below, RMSE, MAE, as well as AIC, AICc, and BIC, ARIMA has the lowest values on the test data than the ETS model.
```{r}
#Accuracy
italy_accuracy_a <-accuracy(forecasts_it_a, test_it)

italy_accuracy_e <-accuracy(forecasts_it_e, test_it)

italy_accuracy_n <-accuracy(forecasts_it_n, test_it)

italy_accuracy_table <- rbind(
  data.frame(italy_accuracy_a),
  data.frame(italy_accuracy_e),
  data.frame(italy_accuracy_n))

```

```{r, warning=FALSE, echo=FALSE}
italy_accuracy_table[ 1:3,1:10] %>%
  kbl() %>%
  kable_paper(full_width = F) %>%
  column_spec(4, color = "white",
              background = spec_color(italy_accuracy_table$RMSE[1:4],end = 0.6)) %>%
    column_spec(5, color = "white",
              background = spec_color(italy_accuracy_table$MAE[1:4],end = 0.6))
```

```{r, warning=FALSE, echo=FALSE}
#AIC
report(data_fit_it_a)
report(data_fit_it_e)

```

### **Residuals**
The output below also suggests that the ARIMA model did well in capturing all the dynamics in data, as the residuals seem to be white noise.
```{r, warning=FALSE}
gg_tsresiduals(data_fit_it_a) + labs(title = "ARIMA Italy residuals analysis")

gg_tsresiduals(data_fit_it_e) + labs(title = "ETS Italy residuals analysis")

gg_tsresiduals(data_fit_it_n) + labs(title = "SNAIVE Italy residuals analysis")
```










