
## 4.4 France{.tabset}

```{r, warning=FALSE}
France_since_2015 <- data_elec %>% select(Date,France) %>% filter(Date >= as.Date("2015-01-01"))
```

### **Testing Models**
Below is the plot of how well each model fits the data based on a 60-period prediction starting from 2016. 
```{r, warning=FALSE}

#Split the data
training_fr <- data_elec %>% select(Date, France) %>%  filter(Date < as.Date("2016-01-01"))
test_fr <- data_elec %>% select(Date, France) %>% filter(Date >= as.Date("2016-01-01"))

# Fit ARIMA model and generate forecasts
data_fit_fr_a <- training_fr %>%
  model(ARIMA(France))
forecasts_fr_a <- data_fit_fr_a %>%
  forecast(h = 60)

# Fit ETS model and generate forecasts
data_fit_fr_e <- training_fr %>%
  model(ETS(France))
forecasts_fr_e <- data_fit_fr_e %>%
  forecast(h = 60)

# Fit seasonal naive model and generate forecasts
data_fit_fr_n <- training_fr %>%
  model(SNAIVE(France))
forecasts_fr_n <- data_fit_fr_n %>%
  forecast(h = 60)

# Combine forecasts into a single data frame
all_forecasts_fr <- bind_rows(
  data.frame(Date = forecasts_fr_a$Date, Method = "ARIMA", Forecast = forecasts_fr_a$.mean),
  data.frame(Date = forecasts_fr_e$Date, Method = "ETS", Forecast = forecasts_fr_e$.mean),
  data.frame(Date = forecasts_fr_n$Date, Method = "SNAIVE", Forecast = forecasts_fr_n$.mean))


# Plot all three sets of forecasts together
data_elec %>% autoplot(France) +
  geom_line(data = all_forecasts_fr, aes(x = Date, y = Forecast, color = Method)) +
  labs(title = "Electricity Demand in France")

```

### **Measuring Model Accuracy**
According to the accuracy table below, RMSE, MAE, and other indicators, ETS has the lowest values on the test data. However, ARIMA has lower values of AIC = 2558.88, AICc = 2559.46, and BIC=2582.07 than the ETS model. 
```{r}
#Accuracy
france_accuracy_a <-data_fit_fr_a %>%
  refit(test_fr) %>%
  accuracy()

france_accuracy_e <-data_fit_fr_e %>%
  refit(test_fr) %>%
  accuracy()

france_accuracy_n <-data_fit_fr_n %>%
  refit(test_fr) %>%
  accuracy()

france_accuracy_table <- rbind(
  data.frame(france_accuracy_a),
  data.frame(france_accuracy_e),
  data.frame(france_accuracy_n))



#AIC
report(data_fit_fr_a)
france_accuracy_table
report(data_fit_fr_e)

```

### **Residuals**
The output below also suggests that the ARIMA model did well in capturing all the dynamics in data, as the residuals seem to be white noise.
```{r}
gg_tsresiduals(data_fit_fr_a) + labs(title = "ARIMA France residuals analysis")

gg_tsresiduals(data_fit_fr_e) + labs(title = "ETS France residuals analysis")

gg_tsresiduals(data_fit_fr_n) + labs(title = "SNAIVE France residuals analysis")
```

















