
## 4.4 France{.tabset}

```{r, warning=FALSE}
France_since_2015 <- data_elec %>% select(Date,France) %>% filter(Date >= as.Date("2015-01-01"))
```

### **Testing Models**
Below is the plot of how well each model fits the data based on a 60-period prediction starting from 2016. 
```{r, warning=FALSE}

#Split the data
training_fr <- data_elec %>% select(Date, France) %>%  filter(Date < as.Date("2016-01-01"))
test_fr <- data_elec %>% select(Date, France) %>% filter(Date >= as.Date("2016-01-01"))

# Fit ARIMA model and generate forecasts
data_fit_fr_a <- training_fr %>%
  model(ARIMA(France))
forecasts_fr_a <- data_fit_fr_a %>%
  forecast(h = 60)

# Fit ETS model and generate forecasts
data_fit_fr_e <- training_fr %>%
  model(ETS(France))
forecasts_fr_e <- data_fit_fr_e %>%
  forecast(h = 60)

# Fit seasonal naive model and generate forecasts
data_fit_fr_n <- training_fr %>%
  model(SNAIVE(France))
forecasts_fr_n <- data_fit_fr_n %>%
  forecast(h = 60)

# Combine forecasts into a single data frame
all_forecasts_fr <- bind_rows(
  data.frame(Date = forecasts_fr_a$Date, Method = "ARIMA", Forecast = forecasts_fr_a$.mean),
  data.frame(Date = forecasts_fr_e$Date, Method = "ETS", Forecast = forecasts_fr_e$.mean),
  data.frame(Date = forecasts_fr_n$Date, Method = "SNAIVE", Forecast = forecasts_fr_n$.mean))


# Plot all three sets of forecasts together
data_elec %>% autoplot(France) +
  geom_line(data = all_forecasts_fr, aes(x = Date, y = Forecast, color = Method)) +
  labs(title = "Electricity Demand in France")

```

### **Measuring Model Accuracy**
According to the accuracy table below, RMSE, MAE, and other indicators, ETS has the lowest values on the test data. However, ARIMA has lower values of AIC, AICc, and BIC than the ETS model. 
```{r}
#Accuracy
france_accuracy_a <-accuracy(forecasts_fr_a, test_fr)

france_accuracy_e <-accuracy(forecasts_fr_e, test_fr)

france_accuracy_n <-accuracy(forecasts_fr_n, test_fr)

france_accuracy_table <- rbind(
  data.frame(france_accuracy_a),
  data.frame(france_accuracy_e),
  data.frame(france_accuracy_n))

```

```{r, warning=FALSE, echo=FALSE}
france_accuracy_table[ 1:3,1:10] %>%
  kbl() %>%
  kable_paper(full_width = F) %>%
  column_spec(4, color = "white",
              background = spec_color(france_accuracy_table$RMSE[1:4],end = 0.6)) %>%
    column_spec(5, color = "white",
              background = spec_color(france_accuracy_table$MAE[1:4],end = 0.6))
```

```{r, warning=FALSE, echo=FALSE}
#AIC
report(data_fit_fr_a)
report(data_fit_fr_e)

```

### **Residuals**
The output below also suggests that the ARIMA model did well in capturing all the dynamics in data, as the residuals seem to be white noise.
```{r}
gg_tsresiduals(data_fit_fr_a) + labs(title = "ARIMA France residuals analysis")

gg_tsresiduals(data_fit_fr_e) + labs(title = "ETS France residuals analysis")

gg_tsresiduals(data_fit_fr_n) + labs(title = "SNAIVE France residuals analysis")
```

















